Generative Adversarial Networks

### 2017-12-02 cs6735/project/draft.tex
finished image generation

\begin{figure}
\centering
\includegraphics[scale=0.55]{img2img}
\caption{Examples of the image-to-image technique developed by Isola \textit{et al.} \citep{2016arXiv161107004I}. This technique makes use of conditional generative adversarial networks to map across image domains.}
\label{fig:Image to Image Examples}
\end{figure}

@@

\subsection{Image Generation}
\subsection{Image to Image Translation} \label{sec:img2img}
\subsection{Super Resolution}
\subsection{Reinforcement Learning}
Reinforcement learning

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.55]{img2img}
\caption{Examples of the image-to-image technique developed by Isola \textit{et al.} \citep{2016arXiv161107004I}. This technique makes use of conditional generative adversarial networks to map across image domains.}
\label{fig:img2img}
\end{figure}

@@

\subsection{Image Generation} \label{sec:img2img}
Image generation is extremely useful as many tasks intrinsically require the ability to generate realistic samples \citep{2017arXiv170100160G}. Most research conducted with respect the GANs attempts to improve the quality of the synthesized images \citep{2017arXiv171007035C}. As such, several useful and fascinating applications have already been found.

Image super-resolution is the process of generating a high resolution image from a lower resolution image by inferring details. For each sample, there are multiple possible outputs. Due to this characteristic, GANs are optimally suited for this task to due their ability to model multi-model outputs. The SRGAN model proposed by Ledig \textit{et al.} trains a generator to fool discriminator which attempts to classify real images from super-resolution images \citep{2016arXiv160904802L}. SRGANs infer photo characteristics with respect to domain of training set \citep{2017arXiv171007035C}.

Image-to-image translation has shown astounding progress recently and offers many yet undiscovered applications \citep{2017arXiv170100160G}. This includes to process of translating from a source domain $X$ to the target domain $Y$. An example of this process can be visualized in figure \ref{fig:img2img}. Conditional networks are well suited for this task and are used within several different GAN architectures which attempt to solve this problem \citep{2016arXiv161107004I, 2017arXiv171111585W, 2017arXiv170310593Z}. Recent work by Zhu \textit{et al.} demonstrate the feasibility of unpaired image-to-image translation by introducing a cycle consistency loss to enforce $F(G(X)) ≈ X$ where $G$ is the mapper and $F$ is the inverse mapper \citep{2017arXiv170310593Z}. Furthermore, research recently released by Wang \textit{et al.} further improve the quality of synthesized images \citep{2017arXiv171111585W}. Generated images from semantic maps are now almost indistinguishable from real images.

\subsection{Reinforcement Learning}
Reinforcement learning
